A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-03-07 paper/paper1/ms.tex
Orbital shear versus stellar wind confinement, remove junk text

Stellar wind confinement...

@@

@@

An even more existential limit arises when we consider the assumptions of the isothermal Parker wind model, and the extreme geometry of \hatpb.  Figure \ref{fig:murrayClaySchematic} shows a schematic modeled after Figure 8 from \citet{2009ApJ...693...23M}.  The point at which the gas velocity exceeds the sound speed, the so-called sonic point, resides at 1.2 $R_p$, a mere $\sim9$ atmospheric scale heights from the planet surface.  The smallness of this radius can be understood from the significant effect of tidal gravity and the .  The pressure level here would be in the fractions of a millibar level, with an atmospheric temperature $\le T_\mathrm{eq}\sim10^3$~K and not yet the $T\sim10^4$~K exosphere range.  Depending on the mass loss rate, the transition from primarily neutral to primarily ionized plasma may occur outside or inside the sonic radius.

>>>>

@@

Stellar wind confinement arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.  A trailing tail may be present, but would not undergo the same boost in density, and would be rapidly carried away by the stellar wind.  This asymmetry could yield the appearance of a leading tail even if mass loss proceeds isotropically, or the asymmetry could be reinforced by an additional dayside/nightside asymmetry.  Examples of this asymmetry can be seen in 3D MHD modeling of WASP 107~b \citep{2022ApJ...926..226M}.

@@
